Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-07-17 main.tex
Update on Overleaf.

    \item 
    We prove an auxiliary result. 
    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
    The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
    Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
    we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
    By the Jordan-Brouwer separation theorem~\cite{}, $Y \setminus (X \cup \{y\})$ has got two connected components,
    and thus $Y \setminus X$ has got two connected components.

@@

Having discussed vector analysis, we review exterior calculus. 
We give a brief introduction into this topic, and refer to the literature for further background~\cite{...}. 
Let $V$ be a real vector space. 
Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
if 
\[ 
    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
    = 
    \text{sign}(\pi) 
    u( v_1, v_2, \ldots, v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.

@@

    We want to estimate norms. 
    Lemma~\ref{lemma:todo} gives 
    \begin{align*}
        \| w''_{m} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
        \\&
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    We also employ Lemma~\ref{lemma:volumecomparison} to find 
    \begin{align*}
        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
        \| \Jacobian \Xi   \|
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        \leq 
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    Putting this all together, 
    \begin{align*}
        &
        \| w_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq  
        \| w'_{m} \|_{L^{p}(T_{m})}
        + 
        \| w''_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \left( 
            \| \cartan u \|_{L^{p}(T_{m})} 
            + 
            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        \right) 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(T_{m})} 
        + 
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(T_{m})} 
        + 
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(U_{m-1})} 
%         \\&
%         \leq  
%         \rho(\calT)^{\frac 1 p} 
%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
%         + 
%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
%         \| \cartan u \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
\end{proof}

>>>>

    \item 
    We recall an auxiliary result.
    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
    As a consequence of the Jordan-Brouwer separation theorem~\cite[Corollary 5.24]{mayer1989algebraische}~\cite[Corollary 6.4]{massey1981algebraic}, 
    we know that $Y \setminus X$ has got two connected components.

    \item 
    We prove an auxiliary result. 
    Suppose that $Y$ is a topological space homeomorphic to a sphere of dimension $m$ and that $X \subseteq Y$ is homeomorphic to a sphere of dimension $m-1$, where $m \geq 1$. 
    The embedding of $X$ into $Y$ cannot be onto~\cite[Theorem~2.55]{lee2011topological}, and so there exists $y \in Y \setminus X$. 
    Using the homeomorphism from $Y$ into the $m$-sphere, which maps $y$ to the northpole without loss of generality, and a stereographic projection, 
    we see that $Y \setminus \{y\}$ is homeomorphic to $R^{m}$.
    As a consequence of the Jordan-Brouwer separation theorem~\cite[Theorem 5.23]{mayer1989algebraische}~\cite[Corollary 5.24]{mayer1989algebraische}~\cite[Corollary 6.4]{massey1981algebraic}, $Y \setminus (X \cup \{y\})$ has got two connected components,
    and thus $Y \setminus X$ has got two connected components.

@@

Having discussed vector analysis, we review exterior calculus. 
We give a brief introduction into this topic, and refer to the literature for further background~\cite{lee2012smooth}. 
Let $V$ be a real vector space. 
Given an integer $k \geq 0$, we let $\Alt^{k}(V)$ denote the space of scalar-valued antisymmetric $k$-linear forms over $V$. 
Recall that any $k$-linear scalar-valued form $u$ over $V$ is called antisymmetric
if 
\[ 
    u( v_{\pi(1)}, v_{\pi(2)}, \ldots, v_{\pi(k)} ) 
    = 
    \text{sign}(\pi) 
    u( v_1, v_2, \ldots, v_k ) 
\]
for any $v_1, v_2, \dots, v_k \in V$ and any permutation $\pi$ of the indices \(\{1, 2, \ldots, k\}\). 
By definition, $\Alt^{1}(V)$ is just the dual space of $V$, and $\Alt^{0}(V)$ is the space of real numbers. 
Formally, we define $\Alt^{k}(V)$ to be the zero vector space when $k < 0$.

@@

    We want to estimate norms. 
    Lemma~\ref{lemma:mixedbconsimplex:exteriorderivative} gives 
    \begin{align*}
        \| w''_{m} \|_{L^{p}(T_{m})} 
        &
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u - \cartan w'_{m} \|_{L^{p}(T_{m})}.
        \\&
        \leq 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan u      \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},k,p} \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    We also employ Lemma~\ref{lemma:volumecomparison} to find 
    \begin{align*}
        \| \cartan w'_{m} \|_{L^{p}(T_{m})}
        &\leq 
        |\det(\Jacobian \Xi  )|^{-\frac 1 p} 
        \| \Jacobian \Xi   \|
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        \leq 
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        \cdot 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})}
        .
    \end{align*}
    Putting this all together, 
    \begin{align*}
        &
        \| w_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq  
        \| w'_{m} \|_{L^{p}(T_{m})}
        + 
        \| w''_{m} \|_{L^{p}(T_{m})}
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \left( 
            \| \cartan u \|_{L^{p}(T_{m})} 
            + 
            \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        \right) 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(T_{m})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan w'_{m} \|_{L^{p}(T_{m})} 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(T_{m})} 
        + 
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan w_{m-1} \|_{L^{p}(U_{m-1})} 
        \\&
        \leq  
        \rho(\calT)^{\frac 1 p} 
        \| w_{m-1} \|_{L^{p}(U_{m-1})} 
        + 
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(T_{m})} 
        + 
        \rho(\calT)^{\frac 1 p} \xi(\calT)
        C_{{\rm PF},T_{m},\Gamma_{m},p} 
        \| \cartan u \|_{L^{p}(U_{m-1})} 
%         \\&
%         \leq  
%         \rho(\calT)^{\frac 1 p} 
%         \| w_{m-1} \|_{L^{p}(U_{m-1})} 
%         + 
%         \left( 1 + \rho(\calT)^{\frac 1 p} \xi(\calT) \right) 
%         C_{{\rm PF},T_{m},\Gamma_{m},p} 
%         \| \cartan u \|_{L^{p}(T_{m})} 
        .
    \end{align*}
    The existence of $w \in W^{p}\Alt^{k}(\Omega)$ satisfying the recursive estimate follows. 
\end{proof}
